A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2025-08-02 paper/restruct-new.tex
restruct-new: NFC style changes

\documentclass[a4paper,english,cleveref,autoref,thm-restate]{article}

\usepackage[utf8x]{inputenc}
\usepackage{t1enc}

\usepackage{hyperref}
%\usepackage{proof}
\usepackage{fullpage}
\usepackage{amssymb}
\usepackage{stmaryrd}
%\usepackage{txfonts}
\usepackage{url}

\usepackage{xcolor}
%\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{yfonts}
\usepackage{tikz}
\usetikzlibrary{cd, arrows}

\newcommand{\Overrightarrow}[2]{\raisebox{#1}{$\ext@arrow 0359\Rightarrowfill@{\mbox{${#2}$}}{}$}}
\newcommand{\Overleftarrow}[2]{\raisebox{#1}{$\ext@arrow 0359\Leftarrowfill@{\mbox{${#2}$}}{}$}}
%\newcommand{\Overrightarrow}[1]{\raisebox{1.4ex}{$\ext@arrow 0359\Rightarrowfill@{\mbox{${#1}$}}{}$}}
\makeatother

\newcommand{\rocq}[1]{(\mbox{\texttt{#1}})}
\newcommand{\highlight}[1]{\emph{#1}}

\newcommand{\imp}{\rightarrow}
\newcommand{\Type}{\mathsf{Type}}
\newcommand{\Set}{\mathsf{Set}}
\newcommand{\Prop}{\mathsf{Prop}}
\newcommand{\refl}[1]{\mathsf{refl}\,{#1}}
\newcommand{\mkmlidtype}[3]{{#1} =^{\mathrm{id}}_{#2} {#3}}
\newcommand{\mkmleqdep}[3]{{#1} =^{\mathrm{dep}}_{#2} {#3}}
\newcommand{\hrefl}[1]{\mathsf{refl^{\mathrm{dep}}}\,{#1}}
\newcommand{\mluniv}{\mathsf{U}}
\newcommand{\Jdep}[2]{\mathsf{J}\;{#1}\;{#2}}
\newcommand{\unittype}{\ensuremath{\mathsf{unit}}}
\newcommand{\unitpoint}{\ensuremath{\ast}}

\newcommand{\nth}[1]{{#1}^{\mbox{\scriptsize th}}}
\newcommand{\defeq}{\triangleq}

\newcommand{\U}{\ensuremath{\mathsf{{HSet}}}}

\newcommand{\myframe}{\mathit{frame}}
\newcommand{\myframetype}{\mathit{frametype}}
\newcommand{\painting}{\mathit{painting}}
\newcommand{\paintingtype}{\mathit{paintingtype}}
\newcommand{\restrframe}{\mathit{restrframe}}
\newcommand{\restrframetype}{\mathit{restrframetype}}
\newcommand{\restrpainting}{\mathit{restrpainting}}
\newcommand{\cohframe}{\mathit{cohframe}}
\newcommand{\cohpainting}{\mathit{cohpainting}}

@@

\section{The recursive structure of iterated parametricity}

Iterated parametricity (in indexed form) produces a family of type
families of the following form:
\begin{equation*}
  \begin{array}{llr}
    X_0 & :              & \U                                                                        \\
    X_1 & :              & X_0 \times X_0 \rightarrow  \U                                            \\
    X_2 & : \Pi a b c d. & X_1(a,b) \times X_1 (c,d) \times X_1(a,c) \times X_1 (b,d) \rightarrow \U \\
    \ldots
  \end{array}
\end{equation*}

Such family can be recursively described by the equations given on Table \ref{}.

@@

$$
\begin{array}{llcl}
\myframetype^{n,[0,...,p]} & & : & Type_{l+1} \\
\myframetype^{n,[]} & & \defeq & unit \\
\myframetype^{n,[0,...,p]} & & \defeq & \myframetype^{n,[0,...,p-1]} \times Type_l\\
\\
\paintingtype^{n,[0,...,p]} & (\myframe^{n,[0,...,p]}:\myframetype^{n,[0,...,p]}) & : & Type_{l+1} \\
\paintingtype^{n,[]} & \star & \defeq & unit \\
\paintingtype^{n,[0,...,p]} & (\myframe^{n,[0,...,p]}) & \defeq & \paintingtype^{n,[0,...,p-1]} \times (\myframe^{n,p} \rightarrow Type_l)\\
\end{array}
$$

Formally, this can be described as:
$$
\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!
\begin{array}{llcl}
\myframe^{n,[0,...,p]} &
  \multicolumn{3}{l}{
  \left(\begin{array}{l}
     \myframe^{n-1,[0,...,p-1]}:\myframetype^{n-1,[0,...,p-1]}\\
     \painting^{n-1,[0,...,p-1]}:\paintingtype^{n-1,[0,...,p-1]}(\myframe^{n-1,[0,...,p-1]})\\
     \restrframe^{n,[0,...,p-1]}:\restrframetype^{n,[0,...,p-1]}\\
  \end{array}\right) : \myframetype^{n-1,[0,...,p]}
  }\\
\myframe^{n,[0]} &
   \left(\begin{array}{l}
      \star\\
      \star\\
      \star\\
   \end{array}\right) & \defeq & (\star,unit)\\
\myframe^{n,[0,...,p+1]} &
   \left(\begin{array}{l}
      \myframe^{n-1,[0,...,p]}\\
      \painting^{n-1,[0,...,p]}\\
     \restrframe^{n,[0,...,p]}\\
   \end{array}\right) & \defeq &
   \left(\begin{array}{l}
     \myframe^{n,[0,...,p]}
             \left(\begin{array}{l}
               \myframe^{n-1,[0,...,p-1]}\\
               \painting^{n-1,[0,...,p-1]}\\
               \restrframe^{n,[0,...,p-1]}\\
             \end{array}\right)     ,\\
     \Sigma d:\myframe^{n,[0,...,p]}
             \left(\begin{array}{l}
               \myframe^{n-1,[0,...,p-1]}\\
               \painting^{n-1,[0,...,p-1]}\\
               \restrframe^{n,[0,...,p-1]}\\
             \end{array}\right).\,\\
     \quad \Pi\omega.\,\painting^{n-1,p}(\restrframe^{n,p}(d))\\
   \end{array}\right)\\
\restrframetype^{n,[0,...,p-1]} &
   \multicolumn{3}{l}{
   \left(\begin{array}{l}
      \myframe^{n-1,[0,...,p-1]}:\myframetype^{n-1,[0,...,p-1]}\\
      \painting^{n-1,[0,...,p-1]}:\paintingtype^{n-1,[0,...,p-1]}(\myframe^{n-1,[0,...,p-1]})\\
   \end{array}\right) : Type_{l}
   }\\
\restrframetype^{n,[]} &
   \left(\begin{array}{l}
      \star\\
      \star\\
   \end{array}\right) & \defeq &
   unit\\
\restrframetype^{n,[0,...,p]} &
   \left(\begin{array}{l}
      \myframe^{n-1,[0,...,p]}\\
      \painting^{n-1,[0,...,p]}\\
   \end{array}\right) & \defeq &
   \begin{array}{l}
     \Sigma \restrframe^{n,[0,...,p-1]}\\
     \quad:\restrframetype^{n,[0,...,p-1]}
                \left(\begin{array}{l}
                  \myframe^{n-1,[0,...,p-1]}\\
                  \painting^{n-1,[0,...,p-1]}\\
                \end{array}\right)
                .\,\\
     \Pi q\leq n.\,\Pi \omega.\,\myframe^{n,[0,...,p]}
       \left(\begin{array}{l}
         \myframe^{n-1,[0,...,p-1]}\\
         \painting^{n-1,[0,...,p-1]}\\
         \restrframe^{n,[0,...,p-1]}\\
       \end{array}\right)\\
   \end{array}\\
\end{array}
$$

@@

$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
\begin{tikzcd}
& & & frame^{n,p}(\textcolor{red}{restrframe^{n,k<p}}) \arrow[d] \\
& & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
& & & frame^{n-1,p} \arrow[d] \\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & & & \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] \\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & & \textcolor{red}{frame^{n-2,k<p}} & \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
\end{tikzcd}

@@

$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
\begin{tikzcd}
& & & frame^{n,p} \arrow[d] \arrow[ddr] \\
& & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
& & & frame^{n-1,p} \arrow[d] \arrow[ddr] & \restrframe^{n,k<p}(\textcolor{red}{cohframe^{n,k<p}}) \arrow[d] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & & & \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[d, dotted]\\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & & \textcolor{red}{frame^{n-2,k<p}} & \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
\end{tikzcd}

@@

$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
\begin{small}
\begin{tikzcd}
& & & frame^{n,p} \arrow[d] \arrow[ddr]\\
& & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
& & & frame^{n-1,p} \arrow[d] \arrow[ddr] & \restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & & & \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted]\\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & & \textcolor{red}{frame^{n-2,k<p}} & \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] & \textcolor{red}{cohframe^{n,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
\end{tikzcd}
\end{small}

@@

$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
\begin{small}
\begin{tikzcd}
& & & frame^{n,p} \arrow[d] \arrow[ddr]\\
\painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
\myframe^{n-1,k\geq p} \arrow[d] \arrow[ddr] & & & frame^{n-1,p} \arrow[d] \arrow[ddr] & \restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & & & \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted]\\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & & \textcolor{red}{frame^{n-2,k<p}} & \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] & \textcolor{red}{cohframe^{n,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
\end{tikzcd}
\end{small}

@@

$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
\begin{small}
\begin{tikzcd}
& & & frame^{n,p} \arrow[d] \arrow[ddr]\\
\painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
\myframe^{n-1,k\geq p} \arrow[d] \arrow[ddr] & \restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & & frame^{n-1,p} \arrow[d] \arrow[ddr] & \restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k\geq p}} \arrow[l, dotted] \arrow[d, dotted] & &
   \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] &
   \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted]\\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & \textcolor{red}{cohframe^{n,k\geq p},X_{n-1}} \arrow[l, dotted] &
   \textcolor{red}{frame^{n-2,k<p}} &
   \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
   \textcolor{red}{cohframe^{n,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
\end{tikzcd}
\end{small}

@@

$\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!\!$
\begin{small}
\begin{tikzcd}
& & & painting^{n,p} \arrow[ddlll] \arrow[dddr] \arrow[d, dotted]\\
& & & frame^{n,p} \arrow[d] \arrow[ddr]\\
\painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
\myframe^{n-1,k\geq p} \arrow[d] \arrow[ddr] & \restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & & frame^{n-1,p} \arrow[d] \arrow[ddr] & \restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
\textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k\geq p}} \arrow[l, dotted] \arrow[d, dotted] & &
   \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] &
   \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted]\\
\textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & \textcolor{red}{cohframe^{n,k\geq p},X_{n-1}} \arrow[l, dotted] &
   \textcolor{red}{frame^{n-2,k<p}} &
   \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
   \textcolor{red}{cohframe^{n,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
\end{tikzcd}
\end{small}

>>>>

\documentclass{article}
\usepackage[a4paper, margin=2em]{geometry}

\usepackage{hyperref, amssymb, stmaryrd, url, xcolor, amsmath, graphicx, yfonts, tikz, enumitem}
\usetikzlibrary{cd, arrows}
\setlist[enumerate]{left=0pt,nosep}

\newcommand{\defeq}{\triangleq}
\newcommand{\U}{\ensuremath{\mathsf{{HSet}}}}
\newcommand{\myframe}{\mathit{frame}}
\newcommand{\myframetype}{\mathit{frametype}}
\newcommand{\painting}{\mathit{painting}}
\newcommand{\paintingtype}{\mathit{paintingtype}}
\newcommand{\restrframe}{\mathit{restrframe}}
\newcommand{\restrframetype}{\mathit{restrframetype}}
\newcommand{\restrpainting}{\mathit{restrpainting}}
\newcommand{\cohframe}{\mathit{cohframe}}
\newcommand{\cohpainting}{\mathit{cohpainting}}

@@

\section{The recursive structure of iterated parametricity}
Iterated parametricity (in indexed form) produces a family of type
families of the following form:
\begin{equation*}
  \begin{array}{llr}
    X_0 & :              & \U                                                                        \\
    X_1 & :              & X_0 \times X_0 \rightarrow  \U                                            \\
    X_2 & : \Pi a b c d. & X_1(a,b) \times X_1 (c,d) \times X_1(a,c) \times X_1 (b,d) \rightarrow \U \\
    \ldots
  \end{array}
\end{equation*}

Such family can be recursively described by the equations given on Table ?.

@@

        $$
          \begin{array}{llcl}
            \myframetype^{n,[0,...,p]}  &                                                     & :      & Type_{l+1}                                                               \\
            \myframetype^{n,[]}         &                                                     & \defeq & unit                                                                     \\
            \myframetype^{n,[0,...,p]}  &                                                     & \defeq & \myframetype^{n,[0,...,p-1]} \times Type_l                               \\
            \\
            \paintingtype^{n,[0,...,p]} & (\myframe^{n,[0,...,p]}:\myframetype^{n,[0,...,p]}) & :      & Type_{l+1}                                                               \\
            \paintingtype^{n,[]}        & \star                                               & \defeq & unit                                                                     \\
            \paintingtype^{n,[0,...,p]} & (\myframe^{n,[0,...,p]})                            & \defeq & \paintingtype^{n,[0,...,p-1]} \times (\myframe^{n,p} \rightarrow Type_l) \\
          \end{array}
        $$

        Formally, this can be described as:
        $$
          \begin{array}{llcl}
            \myframe^{n,[0,...,p]}                                     &
            \multicolumn{3}{l}{
              \left(\begin{array}{l}
                        \myframe^{n-1,[0,...,p-1]}:\myframetype^{n-1,[0,...,p-1]}                               \\
                        \painting^{n-1,[0,...,p-1]}:\paintingtype^{n-1,[0,...,p-1]}(\myframe^{n-1,[0,...,p-1]}) \\
                        \restrframe^{n,[0,...,p-1]}:\restrframetype^{n,[0,...,p-1]}                             \\
                      \end{array}\right) : \myframetype^{n-1,[0,...,p]}
            }                                                                                         \\
            \myframe^{n,[0]}                                           &
            \left(\begin{array}{l}
                      \star \\
                      \star \\
                      \star \\
                    \end{array}\right)                                     & \defeq & (\star,unit)      \\
            \myframe^{n,[0,...,p+1]}                                   &
            \left(\begin{array}{l}
                      \myframe^{n-1,[0,...,p]}  \\
                      \painting^{n-1,[0,...,p]} \\
                      \restrframe^{n,[0,...,p]} \\
                    \end{array}\right) & \defeq &
            \left(\begin{array}{l}
                      \myframe^{n,[0,...,p]}
                      \left(\begin{array}{l}
                          \myframe^{n-1,[0,...,p-1]}  \\
                          \painting^{n-1,[0,...,p-1]} \\
                          \restrframe^{n,[0,...,p-1]} \\
                        \end{array}\right)     , \\
                      \Sigma d:\myframe^{n,[0,...,p]}
                      \left(\begin{array}{l}
                          \myframe^{n-1,[0,...,p-1]}  \\
                          \painting^{n-1,[0,...,p-1]} \\
                          \restrframe^{n,[0,...,p-1]} \\
                        \end{array}\right).\, \\
                      \quad \Pi\omega.\,\painting^{n-1,p}(\restrframe^{n,p}(d))     \\
                    \end{array}\right)                    \\
            \restrframetype^{n,[0,...,p-1]}                            &
            \multicolumn{3}{l}{
              \left(\begin{array}{l}
                        \myframe^{n-1,[0,...,p-1]}:\myframetype^{n-1,[0,...,p-1]}                               \\
                        \painting^{n-1,[0,...,p-1]}:\paintingtype^{n-1,[0,...,p-1]}(\myframe^{n-1,[0,...,p-1]}) \\
                      \end{array}\right) : Type_{l}
            }                                                                                         \\
            \restrframetype^{n,[]}                                     &
            \left(\begin{array}{l}
                      \star \\
                      \star \\
                    \end{array}\right)                                     & \defeq &
            unit                                                                                      \\
            \restrframetype^{n,[0,...,p]}                              &
            \left(\begin{array}{l}
                      \myframe^{n-1,[0,...,p]}  \\
                      \painting^{n-1,[0,...,p]} \\
                    \end{array}\right) & \defeq &
            \begin{array}{l}
              \Sigma \restrframe^{n,[0,...,p-1]}                            \\
              \quad:\restrframetype^{n,[0,...,p-1]}
              \left(\begin{array}{l}
                        \myframe^{n-1,[0,...,p-1]}  \\
                        \painting^{n-1,[0,...,p-1]} \\
                      \end{array}\right)
              .\,                                                           \\
              \Pi q\leq n.\,\Pi \omega.\,\myframe^{n,[0,...,p]}
              \left(\begin{array}{l}
                        \myframe^{n-1,[0,...,p-1]}  \\
                        \painting^{n-1,[0,...,p-1]} \\
                        \restrframe^{n,[0,...,p-1]} \\
                      \end{array}\right) \\
            \end{array} \\
          \end{array}
        $$

@@

        \begin{tikzcd}
          & & & frame^{n,p}(\textcolor{red}{restrframe^{n,k<p}}) \arrow[d] \\
          & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
          & & & frame^{n-1,p} \arrow[d] \\
          \textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & & & \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] \\
          \textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & & \textcolor{red}{frame^{n-2,k<p}} & \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
        \end{tikzcd}

@@

        \begin{tikzcd}
          & & & frame^{n,p} \arrow[d] \arrow[ddr] \\
          & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
          & & & frame^{n-1,p} \arrow[d] \arrow[ddr] & \restrframe^{n,k<p}(\textcolor{red}{cohframe^{n,k<p}}) \arrow[d] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
          \textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & & & \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[d, dotted]\\
          \textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & & \textcolor{red}{frame^{n-2,k<p}} & \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
        \end{tikzcd}

@@

        \begin{tiny}
          \begin{tikzcd}
            & & & frame^{n,p} \arrow[d] \arrow[ddr]\\
            & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
            & & & frame^{n-1,p} \arrow[d] \arrow[ddr] & \restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
            \textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & & & \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted]\\
            \textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & & \textcolor{red}{frame^{n-2,k<p}} & \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] & \textcolor{red}{cohframe^{n,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
          \end{tikzcd}
        \end{tiny}

@@

        \begin{tiny}
          \begin{tikzcd}
            & & & frame^{n,p} \arrow[d] \arrow[ddr]\\
            \painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
            \myframe^{n-1,k\geq p} \arrow[d] \arrow[ddr] & & & frame^{n-1,p} \arrow[d] \arrow[ddr] & \restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
            \textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & & & \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted]\\
            \textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & & \textcolor{red}{frame^{n-2,k<p}} & \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] & \textcolor{red}{cohframe^{n,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm]\\
          \end{tikzcd}
        \end{tiny}

@@

        \begin{tiny}
          \begin{tikzcd}
            & & & frame^{n,p} \arrow[d] \arrow[ddr]\\
            \painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
            \myframe^{n-1,k\geq p} \arrow[d] \arrow[ddr] & \restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & & frame^{n-1,p} \arrow[d] \arrow[ddr] & \restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
            \textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k\geq p}} \arrow[l, dotted] \arrow[d, dotted] & &
            \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] &
            \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted]\\
            \textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & \textcolor{red}{cohframe^{n,k\geq p},X_{n-1}} \arrow[l, dotted] &
            \textcolor{red}{frame^{n-2,k<p}} &
            \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
            \textcolor{red}{cohframe^{n,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
          \end{tikzcd}
        \end{tiny}

@@

        \begin{tiny}
          \begin{tikzcd}
            & & & painting^{n,p} \arrow[ddlll] \arrow[dddr] \arrow[d, dotted]\\
            & & & frame^{n,p} \arrow[d] \arrow[ddr]\\
            \painting^{n-1,k\geq p} \arrow[d, dotted] \arrow[dddr] \arrow[dd, bend right=70] & & & painting^{n-1,p} \arrow[ddlll] \arrow[dddll] \arrow[d, dotted] \\
            \myframe^{n-1,k\geq p} \arrow[d] \arrow[ddr] & \restrframe^{n,k\geq p} \arrow[d] \arrow[ddr] \arrow[l, dotted] & & frame^{n-1,p} \arrow[d] \arrow[ddr] & \restrframe^{n,k<p} \arrow[d] \arrow[ddr] \arrow[uul, dotted, shift right=2mm] \arrow[l, dotted]\\
            \textcolor{red}{painting^{n-2,k\geq p}} \arrow[d, dotted] & \textcolor{red}{restrpainting^{n-1,k\geq p}} \arrow[l, dotted] \arrow[d, dotted] & &
            \textcolor{red}{painting^{n-2,k<p}} \arrow[d, dotted] &
            \textcolor{red}{restrpainting^{n-1,k<p}} \arrow[l, dotted] \arrow[d, dotted]\\
            \textcolor{red}{frame^{n-2,k\geq p}} & \textcolor{red}{restrframe^{n-1,k\geq p},X_{n-2}} \arrow[l, dotted] & \textcolor{red}{cohframe^{n,k\geq p},X_{n-1}} \arrow[l, dotted] &
            \textcolor{red}{frame^{n-2,k<p}} &
            \textcolor{red}{restrframe^{n-1,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] &
            \textcolor{red}{cohframe^{n,k<p}} \arrow[l, dotted] \arrow[uul, dotted, shift right=2mm] \\
          \end{tikzcd}
        \end{tiny}
